### 2018-10-15 manuscript.rmd
added landscape plot

@@

>>>>

```{r}
cteno_color = "#F8766D"
poro_color = "#00BA38"
unresolved_color = "#6F94CD"

papers = read_tsv( "tables/papers.tsv" )
datasets = read_tsv( "tables/datasets.tsv" )
analyses = 
	read_tsv( "tables/analyses.tsv", col_types = 'icccccccccclnnnnccc' ) %>%
	mutate( taxon_sampling = factor( taxon_sampling, levels= c( 'Choanimalia', 'Holozoa', 'Opisthokonta' ) ) )

bootstrap_threshold = 90
posterior_prob_threshold = 95

analyses$result = "Unresolved"
analyses$result[ ( analyses$inference == "Bayesian" ) & (analyses$support_porifera_sister >= posterior_prob_threshold) ] = "Porifera-sister"
analyses$result[ ( analyses$inference == "Bayesian" ) & (analyses$support_ctenophora_sister >= posterior_prob_threshold) ] = "Ctenophora-sister"
analyses$result[ ( analyses$inference == "ML" ) &       (analyses$support_porifera_sister >= bootstrap_threshold) ] = "Porifera-sister"
analyses$result[ ( analyses$inference == "ML" ) &       (analyses$support_ctenophora_sister >= bootstrap_threshold) ] = "Ctenophora-sister"
analyses$result = factor( analyses$result )

analyses$model_summary = analyses$model_rate_matrix
long_summary = paste(analyses$model_rate_matrix, analyses$model_equilibrium, sep="+")
analyses$model_summary[ ! is.na(analyses$model_equilibrium) ] = long_summary[ ! is.na(analyses$model_equilibrium) ]
analyses$model_summary[ grepl("WAG", analyses$model_summary) ] = "WAG" # Simplify WAG
analyses$model_summary = factor( analyses$model_summary, levels=c("GTR+CAT", "F81+CAT", "LG", "WAG") )

```

@@

```{r support}

analyses %>% 
	ggplot( aes(x=model_summary, y=taxon_sampling, col=result) ) +
		geom_jitter( width = 0.20, height = 0.20, alpha=0.7, size=2 ) +
		theme_classic()
```
